\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

% Section styling
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}

% Avoid line-break hyphens splitting words (ATS text extraction)
\hyphenpenalty=10000
\exhyphenpenalty=10000

\begin{document}

%==================== HEADER ====================
\begin{center}
    {\LARGE \textbf{Marc-Antoine Ferland}} \\
    Senior Software Engineer $\cdot$ AI Developer Tooling \& Platform \\
    Quebec City, Canada \\
    \href{mailto:me@maferland.com}{me@maferland.com} \quad
    \href{https://github.com/maferland}{github.com/maferland} \quad
    \href{https://linkedin.com/in/marcantoineferland}{linkedin.com/in/marcantoineferland}
\end{center}

%==================== PROFILE ====================
\section*{Profile}
Engineer with 10+ years building web products, now building AI-native developer tooling at Carta: an LLM-evaluation framework and MCP platform architecture other teams build on. Frontend and developer experience are my craft. Most recently I taught engineers across the org to adopt AI coding agents. Deep in TypeScript and React.

%==================== SKILLS ====================
\section*{Skills}
\textbf{AI \& Agents:} LLM-Powered Coding Agents, Agentic Workflows, MCP, LLM Evaluation \& Regression Testing \\
\textbf{Frontend:} TypeScript, React, Component Architecture, State Management \& Data Fetching, Performance Optimization, Testing (Jest, Storybook, Playwright)

%==================== EXPERIENCE ====================
\section*{Experience}

\textbf{Carta} \hfill Dec 2023--Present\\
\textit{Senior Software Engineer II}
\begin{itemize}
    \item Created and lead Verdict, an LLM-evaluation and regression-testing framework for AI agent behavior, adopted by four teams with 74 plugin test suites written against it; it caught four regressions before merge in a single refactor sweep, and Carta's CEO reviewed it personally.
    \item Authored the domain-registry architecture (domain:verb:noun with a discover/fetch gateway) that every Carta MCP tool now follows, publicly credited by the MCP tech lead; built the BM25 tool-search gateway and the platform's core architecture decision records.
    \item Built perf, an internal toolkit that audits carta-web through Datadog APM and auto-opens draft PRs with N+1 query fixes, driving 30 tracked performance fixes across the team.
    \item Led recurring vibe-coding sessions teaching engineers across multiple teams and directors' orgs to adopt AI coding agents, and presented Verdict and the MCP platform to senior leadership including the CEO and a VP of Engineering.
    \item Delivered Carta's International Securities filings end to end: HMRC (UK) and ATO (Australia) equity-scheme reporting, including an LLM autofill pipeline for fillable government document templates.
    \item Led a 3.5-month migration off a legacy data-fetching hook to a react-query pattern across 15 PRs, now used in 224 files and maintained by nine other engineers.
\end{itemize}

\textbf{Tola} \hfill Jul 2022--Dec 2023\\
\textit{Senior Frontend Engineer}
\begin{itemize}
    \item Established design system, Storybook, and visual regression infrastructure.
    \item Delivered fintech product features while standardizing UX patterns.
    \item Rebuilt invoice editor with real-time preview architecture.
    \item Introduced end-to-end type safety improving reliability.
\end{itemize}

\textbf{Capdesk} \hfill Mar 2021--Jul 2022\\
\textit{Senior Frontend Engineer}
\begin{itemize}
    \item Frontend technical lead for the AngularJS to React migration, using a strangler approach while keeping the product shippable.
    \item Built the initial React platform (design system, Storybook, testing setup) adopted across the product.
    \item Mentored engineers on React and TypeScript; enabled backend engineers to contribute confidently to the frontend.
    \item Introduced modern frontend practices that reduced regressions and improved release confidence.
\end{itemize}

\textbf{Fizzer} \hfill Jul 2018--Mar 2021\\
\textit{Senior Frontend Engineer}
\begin{itemize}
    \item Owned frontend architecture and introduced TypeScript.
    \item Rebuilt postcard editor with rich interactive tooling.
    \item Led redesign and SEO platform contributing to web revenue growth from 5\% to 25\%.
\end{itemize}

\textbf{Cortex} \hfill Apr 2017--Jul 2018\\
\textit{Full Stack Developer} \\
Delivered full-stack features across web, mobile, and chatbot platforms.

\textbf{Coveo} \hfill Jun 2015--Apr 2017\\
\textit{Backend Developer} \\
Built cloud microservices on AWS supporting enterprise search workloads at scale.

\end{document}
