\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}

\begin{document}

\begin{center}
    {\LARGE \textbf{Marc-Antoine Ferland}} \\
    Staff Frontend / Product Engineer \\
    Quebec City, Canada \\
    \href{mailto:me@maferland.com}{me@maferland.com} \quad
    \href{https://github.com/maferland}{github.com/maferland} \quad
    \href{https://linkedin.com/in/marcantoineferland}{linkedin.com/in/marcantoineferland}
\end{center}

\section*{Profile}
Staff Frontend / Product Engineer focused on AI-assisted product workflows, TypeScript/React systems, and high-quality developer experience. I combine frontend architecture, product taste, and pragmatic fullstack execution to ship polished systems across complex domains.

\section*{Experience}

\textbf{Carta} \hfill Dec 2023--Present\\
\textit{Senior Frontend Engineer}
\begin{itemize}
    \item Led frontend architecture improvements for complex product workflows, raising consistency across data fetching, caching, and developer experience.
    \item Authored RFCs modernizing UI infrastructure toward a maintainable component platform.
    \item Delivered equity automation workflows across HRIS integrations, partnering tightly with product and design.
    \item Built and refined filtering, saved views, and workflow improvements for high-usage enterprise product surfaces.
    \item Developed AI-assisted engineering workflows and internal tooling practices to speed up product iteration and code review.
\end{itemize}

\textbf{Tola} \hfill Jul 2022--Dec 2023\\
\textit{Senior Frontend Engineer}
\begin{itemize}
    \item Established design system, Storybook, and visual regression infrastructure for a fintech product surface.
    \item Delivered data-heavy product features while standardizing interaction patterns and UX quality.
    \item Rebuilt invoice editor with real-time preview architecture and clearer product feedback loops.
    \item Introduced end-to-end type safety improving reliability across frontend and API boundaries.
\end{itemize}

\textbf{Capdesk} \hfill Mar 2021--Jul 2022\\
\textit{Senior Frontend Engineer}
\begin{itemize}
    \item Frontend technical lead for the AngularJS to React migration, using a strangler approach while keeping the product shippable.
    \item Built the initial React platform: design system, Storybook, testing setup, and frontend conventions.
    \item Mentored engineers on React and TypeScript; enabled backend engineers to contribute confidently to the frontend.
    \item Introduced modern frontend practices that reduced regressions and improved release confidence.
\end{itemize}

\textbf{Fizzer} \hfill Jul 2018--Mar 2021\\
\textit{Senior Frontend Engineer}
\begin{itemize}
    \item Owned frontend architecture and introduced TypeScript across a consumer product with rich editing workflows.
    \item Rebuilt postcard editor with interactive tooling, improving the core creation experience.
    \item Led redesign and SEO platform contributing to web revenue growth from 5\% to 25\%.
\end{itemize}

\textbf{Cortex} \hfill Apr 2017--Jul 2018\\
\textit{Full Stack Developer}
\begin{itemize}
    \item Delivered full-stack features across web, mobile, and chatbot platforms.
    \item Collaborated closely with product and design stakeholders on ambiguous client problems.
\end{itemize}

\textbf{Coveo} \hfill Jun 2015--Apr 2017\\
\textit{Backend Developer}
\begin{itemize}
    \item Built cloud microservices supporting enterprise search workloads.
    \item Worked on distributed AWS infrastructure at scale.
\end{itemize}

\section*{AI Engineering Tooling}
\begin{itemize}
    \item Built Pinpoint, a visual annotation workflow for AI coding agents that turns screenshots into structured implementation feedback.
    \item Built Relay, an AI-agent coordination system for multi-agent workflows.
    \item Developed Claude Code workflows and repo-level agent instructions to improve software delivery quality and repeatability.
\end{itemize}

\section*{Core Strengths}
\begin{itemize}
    \item Staff-level frontend and product architecture
    \item AI-assisted engineering workflows and agent tooling
    \item TypeScript, React, Next.js, design systems, Storybook, testing
    \item Product/design partnership and crisp UX execution
    \item Remote-first collaboration across US and European teams
    \item Bilingual English/French; Canada-based
\end{itemize}

\end{document}
